Flexibility of interactions depends on habitat suitability

### 2019-08-29 paper/manuscript.Rmd
Conditional effects plot a bit smaller in paper
Add figure in manuscript

```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*4, fig.cap = "Conditional effects"}
readd(fig_conditional_effects)
```

```{r model-comparison-table}
loadd(model_ranking)
waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)

@@

>>>>

```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = "Conditional effects"}
readd(fig_conditional_effects)
```

```{r tab-model-comparison-table}
loadd(model_ranking)
waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)

@@

```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = "Random effects"}
readd(fig_random_effects)
```
